---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
rgl::setupKnitr()
```

# dracor

<!-- badges: start -->
<!-- badges: end -->

The goal of **dracor** is to allow decoding of the Draco compressed meshes in R. 
This is done by wrapping the [Draco](https://github.com/google/draco) C++ 
decoding library with the assistance of the [Rcpp package](https://cran.r-project.org/package=Rcpp).

The original motivation for **dracor** was decoding [neuroglancer](https://github.com/google/neuroglancer) meshes of neurons for
example as used by http://flywire.ai/.

## Installation

**dracor** is not yet available from [CRAN](https://CRAN.R-project.org) but you
can install the development version like so:

```{r, eval=FALSE}
remotes::install_github("jefferis/dracor")
```

## Example

This is a basic example using a sample from the draco repository

```{r}
library(dracor)
# get sample file from draco repository
resp=httr::GET('https://github.com/google/draco/blob/master/testdata/car.drc?raw=true')
car.drc=httr::content(resp, 'raw')
car.m3d=dracor::draco_decode(car.drc)
str(car.m3d)
```


[rgl](https://cran.r-project.org/package=rgl) is the most widely used R package
for 3D visualisation. By default we return meshes as rgl `mesh3d` objects, 
which can then be displayed by `rgl` or manipulated by
a range of R packages including [Rvcg](https://cran.r-project.org/package=Rvcg).
```{r, webgl=T}
# install.packages("rgl")
# convert to rgl mesh3d format
rgl::shade3d(car.m3d, col='red')
# set a nice viewpoint
rgl::view3d(theta = 60, fov=0, zoom=.7)
```

## Some details

**dracor** is deliberately intended as a minimal decoder package without any
dependencies besides the Rcpp package. It only accepts raw bytes as input and can produce either an [rgl](https://cran.r-project.org/package=rgl) `mesh3d` object as output or a list containing points and 0-indexed faces. It essentially 
replicates the most basic decoding ability of the `draco_decoder` command line tool.

If you just want something as close as possible as the Draco library would give
then set `mesh3d=FALSE`
```{r}
car.m=dracor::draco_decode(car.drc, mesh3d=FALSE)
str(car.m)
```

## Acknowledgements 

Many thanks to the authors of:

* [Draco library](https://github.com/google/draco) library
* [Rcpp package](https://cran.r-project.org/package=Rcpp)
